Comparison of approaches to using machine learning models to increase the efficiency of the global search algorithm for solving multicriterial problems

### 2024-07-07 2024/OPTIMA/OPTIMA_2024_MCO.tex
before submission

In the first experiment 100 bi-criterial MCO problems have been solved. As the partial criteria, the functions $f(y)$ from \cite{ML_MCO_2023} were taken,
\begin{equation}
    \label{eq:19}
		\begin{matrix}
		  f(y)= -(AB + CD)^{1/2} \\
			AB =(\sum_{i=1}^7{\sum_{j=1}^7{[A_{ij} a_{ij} (y_1,y_2) + B_{ij} b_{ij} (y_1,y_2)])}})^2 \\
			CD =(\sum_{i=1}^7{\sum_{j=1}^7{[C_{ij} a_{ij} (y_1,y_2) - D_{ij} b_{ij} (y_1,y_2)])}})^2 \\
			a_{ij} (y_1,y_2) = \sin(\pi i y_1) \sin(\pi j y_2), \\
			b_{ij} (y_1,y_2) = \cos(\pi i y_1) \cos(\pi j y_2),
		\end{matrix}
\end{equation}
where $0 \leq y_1, y_2 \leq 1$ and parameters $-1 \leq A_{ij},B_{ij},C_{ij},D_{ij} \leq 1$ are independent uniformly distributed random values.

>>>>

In the first experiment 100 bi-criterial MCO problems have been solved. As the partial criteria, the functions $f(y)$ from \cite{ML_MCO_2023} were taken,
\begin{equation}
    \label{eq:19}
		\begin{matrix}
		  f(y)= -(AB + CD)^{1/2}, \\
			AB =(\sum_{i=1}^7{\sum_{j=1}^7{[A_{ij} a_{ij} (y_1,y_2) + B_{ij} b_{ij} (y_1,y_2)])}})^2, \\
			CD =(\sum_{i=1}^7{\sum_{j=1}^7{[C_{ij} a_{ij} (y_1,y_2) - D_{ij} b_{ij} (y_1,y_2)])}})^2, \\
			a_{ij} (y_1,y_2) = \sin(\pi i y_1) \sin(\pi j y_2), \\
			b_{ij} (y_1,y_2) = \cos(\pi i y_1) \cos(\pi j y_2),
		\end{matrix}
\end{equation}
where $0 \leq y_1, y_2 \leq 1$ and parameters $-1 \leq A_{ij},B_{ij},C_{ij},D_{ij} \leq 1$ are independent uniformly distributed random values.
